Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-31 WSSSPE1_report/WSSSPE1_summary_report.tex
Author order change for Krintz et al.

Two of the papers in this group focus on specific facets of software design that are important factors in a project's sustainability but are often addressed only late in the scientific software development cycle, if at all: Wolski et al~\cite{} look at API governance, and Heiland et al~\cite{} discuss maturity models for software security. The other two papers discuss implementation strategies for science from the perspective of facilitating many or all facets of sustainanability-oriented software design for science:  Blanton and Lenhardt\cite{} contrast large projects that have software infrastructue development built-in with cross-training domain scientist PIs in software engineering best practices. Huang and Lapp~\cite{} discuss how various specialized software engineering skills could be turned into shared instrumentation with low barriers to access.

@@

\item Rich Wolski, Chandra Krintz, Hiranya Jayathilaka, Stratos
  Dimopoulos, Alexander Pucher. Developing Systems for API Governance~\cite{Wolski_WSSSPE}

>>>>

Two of the papers in this group focus on specific facets of software design that are important factors in a project's sustainability but are often addressed only late in the scientific software development cycle, if at all: Krintz et al~\cite{Krintz_WSSSPE} look at API governance, and Heiland et al~\cite{Heiland_WSSSPE} discuss maturity models for software security. The other two papers discuss implementation strategies for science from the perspective of facilitating many or all facets of sustainanability-oriented software design for science:  Blanton and Lenhardt\cite{Blanton_WSSSPE} contrast large projects that have software infrastructue development built-in with cross-training domain scientist PIs in software engineering best practices. Huang and Lapp~\cite{Huang_WSSSPE} discuss how various specialized software engineering skills could be turned into shared instrumentation with low barriers to access.

@@

\item Chandra Krintz, Hiranya Jayathilaka, Stratos
  Dimopoulos, Alexander Pucher, Rich Wolski. Developing Systems for API Governance~\cite{Krintz_WSSSPE}
